### 2022-03-13 experiments.tex
copyrights

>>>>

We believe this to be an interesting and representative use-case scenario for a number of reasons.
Firstly, the inverted pendulum is broadly used as a benchmark in control-system literature.
\todo[inline]{Examples}
A key reason for this is that such a relatively simplistic system allows for straightforward reparametrization to obtain varied system dynamics, which in turn makes a broader range of experiments possible.
Secondly, similar, albeit non-Edge-enabled, setups have been a reality in industry for almost two decades, as evidenced by
\todo[inline]{citation here pls}.
Thirdly, although real deployments would most assuredly employ mobile technologies due to the added benefits of mobility and range, the \acp{RTT} offered by these technologies are higher, or at best equal, those offered by WiFi.
4G, for instance, has average \acp{RTT} of around a few hundred milliseconds, which is orders of magnitude greater than the values measured in our scenario, and current 5G deployments offer \ac{RTT} values barely matching the sub-\SI{10}{\milli\second} values we obtain for WiFi.
Thus we argue that using WiFi allows for more experimental freedom, as the system can be tweaked to obtain worse \acp{RTT} more akin to those of mobile technologies while still allowing us the option to study best-case scenarios with very low-latencies.
